\documentclass[11pt]{article}

% Typography
\usepackage{microtype}
\usepackage{parskip}
\usepackage[inline]{enumitem}

% \makeatletter
% \apptocmd{\@openbib@code}
%   {\setlength{\leftmargin}{0em}}
%   {}{\fail}
% \makeatother

% Layout
\usepackage[left=2.0in, right=2in, top=1in]{geometry}
\usepackage[sc]{titlesec}
\usepackage{titling}

\usepackage[colorlinks=true]{hyperref}

% Fonts
\usepackage{fontspec}
\setmainfont{Libertinus Sans}[
  Numbers=OldStyle
]
\newcommand{\abbrev}[1]{{\addfontfeatures{RawFeature=+c2sc}#1}}
\newfontfamily\titlefont[]{Libertinus Serif Display}

\usepackage{unicode-math}
\setmathfont{Libertinus Math}

% \setmonofont{IBM Plex Mono}

% Layout spec
\titleformat{\section}[leftmargin]
{\normalfont\scshape}{\thesection}{1em}{\MakeLowercase}

\titlespacing{\section}{1in}{2.5ex plus .1ex minus .2ex}{0.3in}
\setcounter{secnumdepth}{0}
\pagenumbering{gobble}

% References -> Publications
\renewcommand\refname{Publications \\\&~Preprints}

% Entry consists of left-aligned bold title, right aligned date
\newcommand\institute[2]{%
  \noindent\textbf{#1}\quad\hfill{#2}\\
  }

\newcommand\usc{\textsc{usc}}

\begin{document}

% \begin{center}
  \huge 
  {\titlefont Matthew Finlayson}

  \small
  \href{https://mattf1n.github.io}{\texttt{mattf1n.github.io}}\quad
  \href{mailto:mfinlays@usc.edu}{\texttt{mfinlays@usc.edu}}
  \bigskip
% \end{center}

\section{Education}

\institute{University of Southern California ({\usc})}{2023--}
Viterbi School of Engineering 
\begin{itemize*}
  \item \abbrev{Ph.D.}\ candidate in computer science
  \item Advised by Swabha Swayandipta and Xiang Ren.
\end{itemize*}

\institute{Harvard University}{2015--2021}
John A. Paulson School of Engineering and Applied Sciences 
\begin{itemize*}
  \item \abbrev{A.B.}\ \textit{cum laude} in field, Highest Honors in Computer Science and Linguistics (Joint)
  \item \abbrev{GPA} 3.9 out of 4.0
  \item Advised by Stuart Shieber and Yonatan Belinkov.
\end{itemize*}

\section{Experience}

\institute{\abbrev{UC} Berkeley, Simons Institute for the Theory of Computing}{2025}
Special Year on Large Language Models and Transformers. \\
Visiting student researcher.

\institute{Meta, Generative \abbrev{AI} (\abbrev{GenAI})}{2024}
Research intern, advised by Aasish Pappu.

\institute{The Allen Institute for \abbrev{AI} (\abbrev{AI2}), Aristo}{2021--2023}
Pre-doctoral researcher advised by Peter Clark and Ashish Sabharwal.

\institute{Microsoft, Natural Language Experiences}{2020}
Software engineering intern.

% \institute{Hikma Health, SWE Intern}{Jun.--Aug.\ 2019}
% Developed a mobile electronic health record system for healthcare professionals
% working with refugees.

\begin{thebibliography}{9}
  \vspace{-2\baselineskip}
  \bibitem{betterlmi} \href{https://arxiv.org/abs/2506.17090}{Better Language Model Inversion by Compactly Representing Next-Token Distributions} \\
    Murtaza Nazir, Matthew Finlayson, John X. Morris, Xiang Ren, and Swabha Swayamdipta \\
    \abbrev{NeurIPS} 2025.
  \bibitem{slung} \href{https://arxiv.org/abs/2505.03052}{Teaching Models to Understand (but not Generate) High-risk Data} \\
    Ryan Wang, Matthew Finlayson, Luca Soldaini, Swabha Swayamdipta, and Robin Jia \\
    \abbrev{COLM} 2025.
  \bibitem{rag} \href{https://arxiv.org/abs/2502.10596}{Post-training an LLM for RAG? Train on Self-Generated Demonstrations} \\
    Matthew Finlayson, Ilia Kulikov, Daniel M. Bikel, Barlas Oguz, Xilun Chen, and Aasish Pappu \\
    \abbrev{ArXiv} 2025.
  \bibitem{metadecoding} \href{https://arxiv.org/abs/2406.16838}{From Decoding to Meta-Generation: Inference-time Algorithms for Large Language~Models} \\
    Sean Welleck, Amanda Bertsch, Matthew Finlayson, Hailey Schoelkopf, Alex Xie, Graham Neubig, Ilia Kulikov, Zaid Harchaoui. \\
    \abbrev{TMLR} 2024.
  \bibitem{logits} \href{https://arxiv.org/abs/2403.09539}{Logits of \abbrev{API}-Protected \abbrev{LLMs} Leak Proprietary Information} \\
    Matthew Finlayson,
    Xiang Ren,
    and Swabha Swayamdipta. \\
    \abbrev{COLM} 2024.
  \bibitem{curious} \href{https://arxiv.org/abs/2310.01693}{Closing the Curious Case of Neural Text Degeneration.} \\
    Matthew Finlayson,
    John Hewitt,
    Alexander Koller,
    Swabha Swayamdipta,
    and Ashish Sabharwal. \\
    \abbrev{ICLR} 2024.
  \bibitem{sfc} \href{https://arxiv.org/abs/2305.14596}{Attentiveness to Answer Choices Doesn't Always Entail High \abbrev{QA} Accuracy.} \\
    Sarah~Wiegreffe, Matthew Finlayson, Oyvind Tafjord, Peter Clark, and Ashish~Sabharwal. \\
    \abbrev{EMNLP} 2023.
  \bibitem{decomp}
    \href{https://arxiv.org/abs/2210.02406}{Decomposed Prompting: A Modular Approach for Solving Complex Tasks.} \\
    Tushar~Khot, Harsh Trivedi, Matthew Finlayson, 
    Yao Fu, Kyle Richardson, Peter~Clark, and Ashish~Sabharwal. \\
    \abbrev{ICLR} 2023.
  \bibitem{lila} \href{https://arxiv.org/abs/2210.17517}{L\={\i}la: A Unified Benchmark for Mathematical Reasoning.} \\
    Matthew Finlayson,
    Swaroop~Mishra,
    Pan~Lu,
    Leonard~Tang,
    Sean~Welleck,
    Chitta~Baral,
    Tanmay~Rajpurohit,
    Oyvind~Tafjord,
    Ashish~Sabharwal,
    Peter~Clark,
    and Ashwin~Kalyan. \\
    \abbrev{EMNLP} 2022.
  \bibitem{regset} \href{https://arxiv.org/pdf/2204.09148.pdf}{
      What Makes Instruction Learning Hard?
      An Investigation and a New Challenge in a Synthetic Environment.
    } \\
    Matthew Finlayson, Kyle Richardson, Ashish~Sabharwal, and Peter Clark. \\
    \abbrev{EMNLP} 2022.
  \bibitem{cma}
    \href{https://aclanthology.org/2021.acl-long.144}{Causal Analysis of
    Syntactic Agreement Mechanisms in Neural Language Models.} \\
    Matthew Finlayson,
    Aaron~Mueller,
    Sebastian~Gehrmann,
    Stuart~Shieber,
    Tal~Linzen,
    and Yonatan~Belinkov. \\
    \abbrev{ACL} 2021. 
\end{thebibliography}

\section{Honors}
\institute{National Science Foundation}{2023}
Graduate Research Fellowship Program (\abbrev{GRFP}) honorable mention.

\section{Invited talks}

\institute{Meta Fundamental \abbrev{AI} Research (\abbrev{FAIR})}{2024}
``The state of (meta-)decoding''

\institute{\abbrev{FAIR} \& {\usc} Information Sciences Institute (\abbrev{ISI})}{2024}
``How to find \abbrev{ChatGPT}'s hidden size, and other low-rank logit tricks''

\institute{Carnegie Mellon University Language Technologies Institute}{2024}
``What top-p sampling has to do with the softmax bottleneck.''

\institute{Instituto Superior Técnico (\abbrev{IST}) \& Unbabel Seminar}{2023}
``Comprehensively evaluating \abbrev{LMs} as general-purpose math reasoners''

\institute{Seminar on Formal Languages and Neural Networks (\abbrev{FLaNN})}{2022}
``What can formal languages tell us about instruction learning?''

\institute{Allen Institute for \abbrev{AI} (\abbrev{AI2})}{2022}
``A Unified Benchmark for Mathematical Reasoning''

\section{Service}

\institute{Conference on Neural Information Processing Systems (\abbrev{NeurIPS})}{2024}
Tutorial co-instructor on decoding algorithms for \abbrev{LLMs}.

\institute{Reviewer}{2022--}
\abbrev{ARR}, \abbrev{ACL}, \abbrev{EMNLP}, \abbrev{NeurIPS}, \abbrev{ICLR}, \abbrev{MathNLP}, \abbrev{MATH}-\abbrev{AI}, \abbrev{CoNLL}, \abbrev{COLM}

\institute{Mentor}{2023--}
Masters students: Shahzaib Saqib Warraich \\
Undergraduates: Jacky Mo, Ryan Wang, Murtaza Nazir

\section{Teaching}

\institute{{\usc} \abbrev{CSCI}-544: Applied Natural Language Processing}{2024} 
Teaching Assistant 

\institute{Harvard \abbrev{CS}-51: Abstraction and Design in Computation}{2020--2021} 
Head Teaching Fellow 

\institute{Harvard \abbrev{CS}-187: Computational Linguistics and \abbrev{NLP}}{2019--2020} 
Curriculum developer, Teaching Fellow 

% \section{Software}
% \institute{\href{https://github.com/justinchiu/openlogprobs}{OpenLogProbs}}{2023}
% Retrieves full-vocabulary outputs from \abbrev{API}-protected large language models.

% \institute{\href{https://github.com/mattf1n/ss}{SS.py}}{2023}
% A command-line tool for searching and citing papers through Semantic Scholar.
 
% \section{Other}
% \institute{Harvard First-Year Outdoor Program}{Aug.\ 2018--May 2021}
% Mentored incoming first-year students on week-long backpacking trips.

% \institute{Harvard Sailing Club}{Aug.\ 2018--May 2021}
% Vice President. Taught sailing basics to beginners weekly.

% % \institute{Harvard Outing Club}{Aug.\ 2015--May 2021}
% % Led regular hiking trips to improve outdoor access for Harvard affiliates.

% Computer languages: Python, OCaml \\
% Human languages: English, Tagalog, some Vietnamese, some Spanish.      \\
% Hobbies: surfing, birding, cycling, ortholinear keyboards, sailing. 

\end{document}
